---
title: "ER01-Project : Alcohol and Incomes"
author: "Emma Kerinec, Yannis Gaziello, Nicolas Derumigny"
date: "1 décembre 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Hmisc)
library(ggplot2)
#change the path!
#mydata <- spss.get("/home/ekerinec/Bureau/CoursM1/er01/proj-er01/data/ESS7e02sas.por", use.value.labels=TRUE)
#mydata <- spss.get("C:/Users/cube/Documents/GitHub/proj-er01/data/ESS7e02sas.por", use.value.labels=TRUE)
mydata <- spss.get("/home/guest/proj-er01/data/ESS7e02sas.por", use.value.labels=TRUE)
```

## Information about data

The data come from the European Social Survey year 2014. 
We looked at the consumption of alcohol and income in France. There was 1917 respondent. 

The information that we used are:
Frequency of alcohol drinking.
Frequency of binge drinking.
Quantity of alcohol drink the kast time on a weekday (monday to thursday).
Quantity of alcohol drink the last time on a week-end (friday to sunday).
Their annual income (net income).


Data are weighted to  give a better representation of the entire population.
```{r}

dataFR <- mydata[which(mydata$CNTRY=="France") , ]

persodata <- dataFR[ , c(599, 211, 212, 443 , 210, 214, 213)]
#211-> ALCWKDY et 212 -> ALCWKND et 599 -> DWEIGHT et 443-> HINCTNTA 210-> ALCFREQ et 214 -> ALCBNGE 213 -> ICGNDRA

persodata <- persodata [which(persodata$ALCWKDY<6666),]
persodata <- persodata [which(persodata$ALCWKND<6666),]

#we took back people who never drunk alcohol or who didn't know information.

plt <- ggplot(data=persodata, aes(x=ALCFREQ, fill=HINCTNTA))
plt <- plt + geom_histogram(aes(weight = DWEIGHT), stat="count") + ggtitle("Title")
plt

```

